Parameter Estimation for the CES Model

### 2013-07-19 CES.Rnw
Adding the L-BFGS-B and grid search to CES.Rnw.

In the above example, we obtain $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
which violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$.

>>>>

In the above example, we obtain convergence of the curve-fitting routine.
But, we also obtain an estimate of $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
that violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$. 
This violation leads to $\sigma_1$ (\texttt{E_1_2 (HM)}) being undefined (\texttt{NA})
in the model summary.

To respect the constraints, we can use the \texttt{L-BFGS-B} optimization
method. The default guess parameters are

<<>>=
modelUKQ_LBFGSB <- cesEst(data=dataUK, 
                          yName="iGDP", 
                          xNames=c("iCapStk", "iLabor", "iQ"), 
                          tName="iYear",
                          method="L-BFGS-B")
summary(modelUKQ_LBFGSB)
@

This approach correctly respects the constraints, 
but the \texttt{LM} algorithm does not converge.

To assess what is happening, we can use the built-in grid search
capability of \texttt{cesEst}. Grid search is accessed by specifying
rho or rho1 arguments and a range of values.

<<>>=
modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
modelUKQ_grid <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=1, to=20, by=2), 
                        rho1=seq(from=1, to=2, by=0.2))
summary(modelUKQ_grid)
@

<<>>=
plot(modelUKQ_grid)
@
